\section{Conclusion}
In this paper, we developed a mathematical model to predict the spread of dandelions and evaluate whether they are genuinely invasive. Our seed agent model considers the different phases of a dandelion's life cycle, including seed dispersal, germination, plant development, and the puffball stage. The model also considers environmental factors such as temperature, light, and soil nutrients. The paper discusses the application of the model to three different regions and analyzes the ecological impact and economic potential of other invasive species.

To evaluate foreign species' trade-offs, we formulate an impact score based on ecological and economic factors, which evaluated dandelions and garlic mustard plants as invasive and English ivy plants as simply foreign. Furthermore, our model is adaptable as we provide a unique framework for different regions and foreign plant combinations. 

We hope that our model can be a step forward in understanding how dandelions and other foreign plants can spread in a new environment and aid the understanding of the most impactful environmental factors on dandelion growth. In the future, we aim to share our models with environmental scientists worldwide and fine-tune them to even more region-specific hyperparameters. We also envision that our model can be showcased with an easy-to-use graphical interface, adjustable hyperparameters, and a place for data upload—all of which can significantly benefit foreign species analysis. 